How residence time constrains diversity

### 2015-06-08 analyses/ResTime_GeneralResults.Rmd

```{r, results = 'hide', message = FALSE, warning = FALSE}
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/SimData.csv")  
```

@@

@@

@@

N <- log(sim.data$N)
S <- log(sim.data$S)

@@

N <- sim.data$N
plot(m.tau, log(N), xlab="Cell Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau",
     col='cornsilk4')

S <- sim.data$S
plot(m.tau, log(S), xlab="Cell Residence Time", 
     ylab="Species Richness", 
     main = "S vs. Tau",
     col='darkseagreen')

e.var <- sim.data$e.var
e.simp <- sim.data$simpson.e
plot(m.tau, e.var, xlab="Cell Residence Time", 
     ylab="Species Evenness", 
     main = "Evenness vs. Tau",
     col='skyblue')

avg.ab <- N/S
plot(m.tau, log(avg.ab), xlab="Cell Residence Time", 
     ylab="Average Abundance",
     main = "N/S vs. Tau",
     col='coral')
```

BP <- sim.data$berger.parker
plot(m.tau, BP, xlab="Cell Residence Time", 
     ylab="Berger-Parker", 
     main = "Relative Dominance vs. Tau",
     col='firebrick')

SimpD <- sim.data$inv.simp.D
plot(m.tau, SimpD, xlab="Cell Residence Time", 
     ylab="Simpsons, 1/D", 
     main = "Diversity vs. Tau",
     col='gold')

Skew <- sim.data$skew
plot(m.tau, Skew, xlab="Cell Residence Time", 
     ylab="Skewness", 
     main = "Rarity vs. Tau",
     col='limegreen')

Nmax <- sim.data$N.max
plot(m.tau, log(Nmax), xlab="Cell Residence Time", 
     ylab="Nmax",
     main = "Absolute Dominance vs. Tau",
     col='sandybrown')
```

@@

plot(log(N), Skew, xlab="Total abundance", 
     ylab="Skewness",
     main = "Rarity vs. N",
     col='plum')
```

@@

growth <- sim.data$avg.per.capita.growth
plot(m.tau, log(growth), xlab="Cell Residence Time", 
     ylab="growth", 
     main = "Per capita growth vs. Tau",
     col='dodgerblue')

maint <- sim.data$avg.per.capita.maint
plot(m.tau, SimpD, xlab="Cell Residence Time", 
     ylab="maintenance", 
     main = "Per capita maintenance vs. Tau",
     col='darkolivegreen')

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
rads <- list()
rad.list <- read.table("~/GitHub/hydrobide/results/simulated_data/RADs.csv",
            header = FALSE, sep = ",", col.names = paste0("V", seq_len(1000)),
            as.is = TRUE, skipNul = TRUE, fill = TRUE)

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
species <- list()
species.list <- read.table("~/GitHub/hydrobide/results/simulated_data/Species.csv",
            header = FALSE, sep = ",", col.names = paste0("V", seq_len(1000)),
            as.is = TRUE, skipNul = TRUE, fill = TRUE)

>>>>

```{r, results = 'hide', message = FALSE, warning = FALSE}
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015June/June7/SimData.csv")  
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}

@@

N <- sim.data$N
S <- sim.data$S
e.var <- sim.data$e.var
e.simp <- sim.data$simpson.e
avg.ab <- N/S
Skew <-sim.data$skew
Nmax <- sim.data$N.max
SimpD <- sim.data$SD
```

@@

@@

plot(log(N), Skew, xlab="Total abundance", 
     ylab="Skewness",
     main = "Rarity vs. N",
     col='plum')

@@

@@

growth <- sim.data$avg.per.capita.growth
growth <- (S*growth)/N
x <- c()
y <- c()

ct <- 1
for (val in growth){
  if(is.nan(val) == FALSE && val > 0.1){
    y <- c(y, val)
    x <- c(x, m.tau[ct])
    }
  ct <- ct+1
  }

plot(x, y, xlab="Cell Residence Time", 
     ylab="growth", 
     main = "Per capita growth vs. Tau",
     col='dodgerblue')

maint <- (S*sim.data$avg.per.capita.maint)/N
plot(m.tau, SimpD, xlab="Cell Residence Time", 
     ylab="maintenance", 
     main = "Per capita maintenance vs. Tau",
     col='darkolivegreen')

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
rads <- list()
rad.list <- read.table("~/GitHub/hydrobide/results/simulated_data/2015June/June7/RADs.csv",
            header = FALSE, sep = ",", col.names = paste0("V", seq_len(1000)),
            as.is = TRUE, skipNul = TRUE, fill = TRUE)

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
species <- list()
species.list <- read.table("~/GitHub/hydrobide/results/simulated_data/2015June/June7/Species.csv",
            header = FALSE, sep = ",", col.names = paste0("V", seq_len(1000)),
            as.is = TRUE, skipNul = TRUE, fill = TRUE)
